---
title: "R Notebook"
output: html_notebook
editor_options: 
  markdown: 
    wrap: 72
---

# Data Analytics for Immersive Environments - Grace Reillylibrary

#### Student No. D00262395

## Table of Contents

#### **1.Abstract**

#### **2.Introduction**

-   Topic & Context

-   Rationale & Hypothesis

#### **3.Method**

#### **4.Results**

#### **5.Discussion**

#### **6.References**



#### ** 1.Abstract**

The aim of this study was to determine which, if any is an effective
treatment in PTSD patients. The study divided 150 patients (M= 75, F=75)
into 3 groups using random sampling dependent on the type of treatment
they would receive; Control (traditional CBT, no VR), Static
(non-animated model content, VR), Animated (animated model content, VR).
Treatment consisted of a 50 minute session weekly with their therapist
over 12 weeks. PTSD measurements for all groups were measured using the
observer-rated and self-report mechanisms. Measurements were taken at
the start and end of the study. The main findings include patients OR
and CPSS-SR were significantly decreased post treatment. Graph X shows
that the OR and CPSS-SR measurements are very closely related.
Furthermore X appears to be the most effective for the treatment of
PTSD.

#### ** 2.Introduction**

##### - Rationale & Hypothesis

Post-traumatic stress disorder (PTSD) is observed in humans that have
been exposed to a horrifying event, through direct experience or witness
of such event. Symptoms might include vivid flashbacks, nightmares,
intense distress and severe anxiety. The rationale behind this study is
to understand what the most effective treatment is for PTSD in adults
aged 18-25. 
The **null hypothesis** states no one group had a higher result.
The **alternative hypothesis** states one or all groups had a higher result.

### ** 3.Method**

The method used to analysis the data to derive a conclusion regarding the 
null hypothesis. I began by displaying the data in a bar chart to compare the
values across the different subgroups within the PTSD data.


```{r}
```


```{r}
library(ggplot2)
df <- read_excel("C:/Users/iviic/OneDrive/Desktop/data.xlsx")

data <- data.frame(
    group = c("Static", "Control", "Animated"),
    score_type = c("pre_trial_cpss", "pre_trial_cpss", "pre_trial_cpss",
                   "pre_trial_or", "pre_trial_or", "pre_trial_or",
                   "post_trial_cpss", "post_trial_cpss", "post_trial_cpss",
                   "post_trial_or", "post_trial_or", "post_trial_or"),
    value = c(sum(df$pre_trial_cpss[df$test_group == "Static"]),
              sum(df$pre_trial_cpss[df$test_group == "Control"]),
              sum(df$pre_trial_cpss[df$test_group == "Animated"]),
              sum(df$pre_trial_or[df$test_group == "Static"]),
              sum(df$pre_trial_or[df$test_group == "Control"]),
              sum(df$pre_trial_or[df$test_group == "Animated"]),
              sum(df$post_trial_cpss[df$test_group == "Static"]),
              sum(df$post_trial_cpss[df$test_group == "Control"]),
              sum(df$post_trial_cpss[df$test_group == "Animated"]),
              sum(df$post_trial_or[df$test_group == "Static"]),
              sum(df$post_trial_or[df$test_group == "Control"]),
              sum(df$post_trial_or[df$test_group == "Animated"]))
)

data$group <- factor(data$group, levels = c("Static", "Control", "Animated"))
data$score_type <- factor(data$score_type, levels = c("pre_trial_cpss", "post_trial_cpss", "pre_trial_or", "post_trial_or"))
ggplot(data, aes(x = group, y = value, color = score_type)) +
    geom_col(aes(fill = score_type), position = "dodge", width = 0.8, color = "#000000", linewidth = 1) +
    labs(x = "Bar Chart Test Group", y = "Sum of Scores") +
    scale_color_manual(values = c("#0000FF", "#FF00FF","#FFFF00","#30FF00")) +
    theme(text = element_text(color = "#000000"))

```
#### **4.Results**

#### **5.Discussion**

#### **6.References**



Add a new chunk by clicking the *Insert Chunk* button on the toolbar or
by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output
will be saved alongside it (click the *Preview* button or press
*Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the
editor. Consequently, unlike *Knit*, *Preview* does not run any R code
chunks. Instead, the output of the chunk when it was last run in the
editor is displayed.

From this point
